Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-02 manuscript.tex
Discussion and Conclusion finished

%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 3.55in]{HD12862_[2]gamma_vs_bisspan.pdf} 
\includegraphics[height = 3.65in]{HD12862_[2]RadialVelocityDifferences.pdf} 
   \caption{\emph{Left: }Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B. As we can see with the strong correlation, those two parameters measure the CCF asymmetry in the same way. \emph{Top right:} RVs as function of Julian Day for Alpha Centauri b in 2010. The RVs are retrieved using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan crosses) of a SN density fitted to the CCF. \emph{Bottom right:} RV differences between the RV derived when using the SN density and the RV derived when using the Normal density.}
   \label{fig:alphacent:corr.gamma}
\end{center}
\end{figure*}
%

@@

\xavier{We measured the standard deviation of each CCF parameters for all the CCF of HD215152, HD192310 and Corot-7. This gives us an information of how the noise on each CCF parameter varies as a function of SNR. In this case, the SNR, measured at 550 nm on the original spectra, varies between 10 and 500. The results can be seen in Fig.~\ref{fig:se}. }

@@

\subsection{Estimation of standard errors for the CCF parameters for real stars} \label{sec:bootstrap_real_star}
In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, either defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels. The parameter SN50 corresponds to the SNR in order 50, which defines a wavelength of 550\,nm. In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal density. We first see that the errors on the CCF parameters only depends on the SNR and do not depend on the spectral type. This is true if the spectral type are not too different though, like here where we show the results for G and K dwarfs.

Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.6$ when using SN mean RV and $0.9$ when using SN median RV. In other words, by using SN median RV as parameter that defines the radial velocity of the star given a CCF, we get standard errors $10\%$ smaller than using the Normal fit and its corresponding mean. This result is consistent with what we observed with the simulation from SOAP presented in Sec. \ref{sec:soap}.

Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable. Therefore, the precision in the width of the CCF is the comparable if we fit a Normal or a SN to the CCF.

Finally, for the errors in evaluating the asymmetry of the CCF, we see that, when fitting the SN to the CCF, the asymmetry errors are $15\%$ smaller. Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN. We recall moreover that, using the SN, all parameters are automatically retrieved in 1 single step, while in the common approach the RV and the BIS SPAN are calculated separately.

%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter. When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles). However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN. Note that for the asymmetry, the error in BIS SPAN is in \kms. To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
   \label{fig:se}
\end{center}
\end{figure*}

An analysis of the CCF residuals after fitting a Normal or SN density shows that the SN is a slightly better model to explain the shape of the CCF. This comes from the fact that CCF's present a natural asymmetry due the convective blueshift.

We tested at first our assumptions by using simulated CCF's retrieved using the software SOAP 2.0. We then compared for five real stars the difference between the RV's (defined as mean of a Normal, mean of the SN or median of the SN), FWHM and asymmetry (BIS SPAN in the Normal case and $\gamma$ in the SN case). The $\gamma$ parameter is linearly dependent on the BIS SPAN, with always a strong correlation coefficient. 
%To compare $\gamma$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma$ by the slope of the linear dependence between $\gamma$ and BIS SPAN. 
The slope of this linear correlation changes depending on the studied star. This is probably because the spectral type is different, therefore the effects from stellar activity are different.

When using as parameter for the RV the mean of the SN, the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal. However, once the RV is defined as the median of the SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma$ in the SN case) with respect to the RV's (RV's in the Normal case or SN RV's in the SN case), we observe that the correlations are always stronger for the parameters of the SN. Therefore, the SN parameters are more sensitive to activity. In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.322$ between $\gamma$ and SN mean RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.

In this paper we introduced a novel approach based on the Skew Normal (SN) density to retrieve RV's and shape variations in the CCF of stars. When searching for small-mass exoplanets using the RV technique, it is essential to understand variation of the shape of the CCF, which is a proxy for stellar activity effects. The standard approach consist at first to fit a Normal density to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal density, and then to measure the asymmetry of the CCF by calculating the BIS SPAN. FWHM and BIS SPAN give us information on the line shape that are used to probe stellar activity signals.

In this paper we propose to conduct the analysis fitting a SN density to the CCF. Since the CCF presents a natural asymmetry due the convective blueshift, the SN density can in principle better catch these aspects respect the Normal fit. On top of that, by using the SN density to fit CCF's, we can measure simultaneously the RV of the star, the width and the asymmetry of the CCF.

Starting from the simulation environment SOAP and then moving to real stars, we showed that using the SN density to fit CCF's leads to a significant improvement to probing stellar activity. While for the Normal density mean and median are equivalent, using the SN fit different location parameters can be tested. While the median of the SN is a more robust statistic respect variations in the shape of the CCF, the mean of the SN is more sensible to changes in the asymmetry of the CCF. We suggest to use as parameter that defines the RV of the star the median of the SN, since the standard errors related to this parameter working with CCF's from real stars are on average $10\%$ smaller than the standard errors retrieved using the Normal density. To evaluate changes in the asymmetry of the CCF, we suggest to use the mean of the SN. The correlation between SN mean RV and SN FWHM and the correlation between SN mean RV and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}). The precision on the asymmetry measured by $\gamma$ is greater than the one on BIS SPAN by $\sim$15\%. Therefore when searching for rotational periods in the data, or applying Gaussian Processes to account for stellar activity signals, the SN parameters should be used.

Because of stellar activity the estimated RV's are contaminated by spurious variations. We propose to use a function that corrects from stellar activity that beyond the width and the asymmetry parameters of the CCF includes also the contrast parameter A and the fourth parameter defined as the interaction between width and the asymmetry parameters of the CCF. We found these new two parameter helpful to explain part of the spurious variations in RV's caused by stellar activity.

Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low SNR regime where a gain of 50\% can be reached. This takes significantly more time, but note that 100 bootstrapped dataset are enough to get a good estimation of errors.

\small{
\begin{table}[!t]
\scalebox{0.45}{
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{SN mean RV})$} & \textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
\hline
 $\text{HD}192310  $          &    $1577$    & $0.888$ & $0.786$ & $0.669 (0.64; 0.695)$ & $0.329 (0.285; 0.373)$  & $-0.333 (-0.376; -0.289)$ & $0.666 (0.637; 0.692)$ & $0.476 (0.4367 0.514)$\\
\hline
 $\text{HD}10700 $            &    $7928$    & $0.78$ & $0.604$ & $0.322 (0.302; 0.342)$ & $-0.073 (-0.095; -0.0051)$ & $0.127 (0.105; 0.148)$ & $0.421 (0.403; 0.439)$ & $0.529 (0.513; 0.545)$ \\
\hline
 $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $0.794$ & $0.571 (0.485; 0.646)$ & $-0.067 (-0.184; 0.052)$  & $0.269 (0.155; 0.376)$ & $0.210 (0.094; 0.321)$ & $-0.138 (-0.253; -0.020)$ \\
\hline
 $\text{Corot }7$     &     $173$    &  $0.814$  & $0.607$ & $0.561 (0.450; 0.656)$ & $0.092 (-0.058; 0.238)$ & $-0.335 (-0.228; -0.082)$ & $-0.709 (0.626;0.776)$ & $0.595 (0.489; 0.683)$ \\
\hline
\end{tabular}
}
\caption{Subset of notable correlations between the asymmetry parameter (and the FWHM) and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$. The complete results of the analyses of the correlations for the four stars are presented in Fig. \ref{fig:Gliese785:corrPlot}--\ref{fig:Corot7:corrPlot}.}
\label{table:summaryStars}
\end{table}
}

>>>>

%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 3.6in]{HD12862_gamma_vs_bisspan.pdf} 
\includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
   \caption{\emph{Left: }Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B. As we can see with the strong correlation, those two parameters measure the CCF asymmetry in the same way. \emph{Top right:} RVs as function of Julian Day for Alpha Centauri b in 2010. The RVs are retrieved using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan crosses) of a SN density fitted to the CCF. \emph{Bottom right:} RV differences between the RV derived when using the SN density and the RV derived when using the Normal density.}
   \label{fig:alphacent:corr.gamma}
\end{center}
\end{figure*}
%

@@

\xavier{We measured the standard deviation of each CCF parameters for all the CCF of HD215152, HD192310 and Corot-7. This gives us an information of how the noise on each CCF parameter varies as a function of SNR. In this case, the SNR, measured at 550 nm on the original spectra, varies between 10 and 500. The results can be seen in Fig.~\ref{fig:se}. In the top plots of this figure, we show the standard errors for the different RV, width and asymmetry estimates. Note that because BIS SPAN and $\gamma$ does not have the same units, we used the slope of the correlation between those two parameters to transform $\gamma$ in \ms (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star). In the bottom plots, we show the ratio between the standard errors measured when using the SN parameters and the Normal parameters. Values smaller or larger than one will imply that standard errors fro the SN parameters are more or less precise, respectively.}

\xavier{Looking at the estimates for the RV, we see that they all follow a similar exponential decay. Although we plot the data for three different stars, we do not see any offsets in this decay, which implies that the SNR at 550 nm is the main contributor to the precision measured in RV. This is not surprising as the 3 stars studies are all main sequence K-dwarfs. When comparing the three different estimates for the RV, we see that SN mean RV presents standard errors that are 60\% larger than what N mean RV gives. On the opposite, SN median RV gives errors 10\% more precise than N mean RV. Regarding the parameters describing the width of the CCF, FWHM and SN FWHM have the same standard errors. Finally, for the asymmetry parameters, we see that $\gamma$, derived from the SN, is 15\% more precise than BIS SPAN. In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV, we are able to improve by 10\% the precision on the RV, 15\% the precision on the asymmetry, and this without degrading the precision on the width estimate. SN mean RV should not be use to derive RVs, except perhaps for stars for which the photon noise is not the dominant source of noise, as the precision on this parameter if 60\% worse than the precision on the RV derived from a Normal density fit.}
%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter. When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles). However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN. Note that for the asymmetry, the error in BIS SPAN is in \kms. To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
   \label{fig:se}
\end{center}
\end{figure*}

\xavier{When fitting a SN density to the CCF, it is possible at once to retrieve parameters that describe the RV, i.e. the CCF barycenter, the amplitude, also called the contrast, the width, and the asymmetry of the CCF. For the RV, we investigated the use of the mean and the median of the SN density. Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry, by using $\gamma$, the skewness parameter of the SN density.

When we tested the SN density fit to the CCF provided by the SOAP 2.0 code, that simulate the activity signal induced by a spot or a faculae on a solar-like star, we arrived to the conclusion that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual method. By more sensitive, we mean here that the correlation between the skewness and either the mean or median of the SN density is stronger than between BIS SPAN and the mean of a Normal density. Moreover, the correlation between the FWHM and the CCF barycenter is also stronger when using the parameters from the SN compared to the parameters from the Normal. We also confirmed the behavior that the SN parameters are more correlated than the Normal parameters in the case where a planetary signal is added the to stellar activity modeled by SOAP 2.0.

We also present in this paper a new function to correct for stellar activity signals. Generally, when fitting for planetary signals, people use a model composed of one or several Keplerians to account for the planets, in addition to a linear combination with the FWHM and BIS SPAN of the CCF to account for stellar activity signals. The new function propose to add a linear dependency with the amplitude of the CCF retrieved either by the SN or Normal density fit, and a interaction term between the asymmetry and the width parameters. On the simulated data from SOAP 2.0, this new model allows to mitigate stellar activity signals by a factor of 2 and 3.5 compared to the model generally used, for the faculae and spot, respectively.

When moving to real data, we arrived to the same conclusions regarding the strength of the correlation between the asymmetry and the CCF barycenter, as well as between the width and the CCF barycenter. We note however that although in the case of the simulated data, the stronger asymmetry-RV correlation was found between $\gamma$ and the median of the SN, in the case of real data, it was between $\gamma$ and the mean of the SN. This can be due to the fact that in SOAP 2.0, the faculae is not modelled properly, as it uses as emerging spectrum the one from a spot. We know that the temperature between a spot and a faculae is significantly different, therefore their spectra should be different. In addition, there is always several active regions on a star, at different locations in longitude and latitude. This could also be responsible for the fact that we do not observe the same behavior for the mean and the median of the SN when we compare the SOAP 2.0 simulation and real data. Nevertheless, in both the simulated case and the real cases, the parameters derived from the SN are more sensitive to activity than the parameters derived from a Normal fit. In addition, the correlation between the asymmetry and the mean of the SN is always stronger than any other parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.

When comparing the different RV estimates obtained from the mean of the Normal density, the mean or the median of the SN density, we see that in the case of real data, the amplitude of stellar activity is larger for the mean of the SN, followed by the median of the SN and the mean of the Normal. Although there is a huge gap between the first and the second estimate, the difference between the second and the third is much smaller. The mean of the SN density is therefore more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal, which is not surprising as the SN density is able to model the asymmetry of the CCF, what the Normal density does not.

Having an estimate of the RV that is more sensitive to stellar activity, like the mean of the SN, can help us to probe better stellar rotational periods, or understand better the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}. We saw in the preceding section that the RV estimated by the mean of the SN is 60\% noisier than the RV derived by the mean of the Normal. This is not necessarily a negative aspect. Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized by increasing its induced RV amplitude even if the white noise is 60\% larger.

Even if the different RV estimates have different amplitudes, once we apply our new correction for stellar activity, we arrive exactly to the same RV rms in the residuals, meaning that for activity correction, the SN parameters does not help. We note that when comparing the activity correction presented in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, we only see a slight improvement brought by our proposed correction.

We checked if some RV estimates were better at finding planets in RV data affected by observed stellar signals. When using the new correction proposed in this paper to mitigate the effect from stellar activity, and when assesing planetary detection based on periodogram analysis, we find very similar detection limits for the three RV estimates presented in this paper. Therefore it seems that any of the RV estimate can be used to search for planetary signals.

Finally, we investigated the precision of each of the SN and Normal parameters including the BIS SPAN. It turns out that the mean of the SN should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than when taking the mean of the Normal distribution. However, the median of the SN should be used, as it is 10\% more precise than the mean of the Normal. Regarding the asymmetry estimates, we observe that $\gamma$ has a precision15\% better than the BIS SPAN. It is therefore clear in this case that the SN parameters are more precise to measure the barycenter and the asymmetry of the CCF.}

%Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low SNR regime where a gain of 50\% can be reached. This takes significantly more time, but note that 100 bootstrapped dataset are enough to get a good estimation of errors.

\xavier{When searching for small-mass exoplanets using the RV technique, it is crucial to get the best precision possible on the determination of the RV, but also to measure precisely the shape variations of the CCF, as such variations are induced by stellar activity, and not by planets. The correlations between the width of the CCF and the RV, and the asymmetry of the CCF and the RV are used as a way to assess if the measurements are affect by stellar activity signals, therefore, the stronger the correlation, the better we can probe small level of stellar activity.

In this paper we introduced a novel approach based on the Skew Normal (SN) density to retrieve the RV and shape variation of the CCF. This new method is compared to the usual one, where a Normal density is fitted to the CCF to retrieve the information on the RV and the width of the CCF, and a bisector analysis allows to retrieve the asymmetry of the CCF using the BIS SPAN. In addition, we also compare this novel approach to other parameterisations of the CCF asymmetry that have been shown to be more sensitive to activity signals \citep[][]{Boisse-2011,Figueira-2013}.

In all the different tests we could conduct in this paper, the SN parameters were doing as well as the parameters derived when fitting a Normal distribution and calculating the BIS SPAN.
Moreover, in some cases, we were getting better results when using the SN parameters. This is the case when looking at the correlations between the CCF asymmetry and the RV or the CCF width and the RV. The SN parameters $\gamma$, SN FWHM and the mean of the SN density always show stronger correlation that any of the parameters derived by the Normal density fit and the BIS SPAN, or the different asymmetry parametrization presented in \citet{Boisse-2011} and \citet{Figueira-2013}. Those SN parameters can therefore probe better stellar activity signals. In addition, the precision measured on the median of the SN density and the asymmetry of the SN density are 10 and 15\% more precise than the mean of the Normal and BIS SPAN, respectively.

Because of these advantages of using the SN parameters compared to the Normal parameters, BIS SPAN, and all the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}. we strongly encourage the community of using this new parametrization of the CCF.
Correlations between the asymmetry and the mean of the SN, and between the width and the mean of the SN should be used to probe better stellar signals in RV data, and the median of the SN should be used as the new definition for RV.
}

\small{
\begin{table*}[!t]
\caption{Subset of notable correlations between the asymmetry parameter (and the FWHM) and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$. The complete results of the analyses of the correlations for the four stars are presented in Fig. \ref{fig:Gliese785:corrPlot}--\ref{fig:Corot7:corrPlot}.}
\begin{tabular}{ccccccccc}
\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{SN mean RV})$}\\
\hline
\hline
 $\text{HD}192310  $          &    $1577$    & $0.888$ & $0.786$ & $0.669 (0.64; 0.695)$\\
\hline
 $\text{HD}10700 $            &    $7928$    & $0.78$ & $0.604$ & $0.322 (0.302; 0.342)$\\
\hline
 $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $0.794$ & $0.571 (0.485; 0.646)$ \\
\hline
 $\text{Corot }7$     &     $173$    &  $0.814$  & $0.607$ & $0.561 (0.450; 0.656)$  \\
\hline
\rule{0pt}{2ex}    & & & &\\
\textbf{Star}          &\textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
\hline
\hline
 $\text{HD}192310  $& $0.329 (0.285; 0.373)$  & $-0.333 (-0.376; -0.289)$ & $0.666 (0.637; 0.692)$ & $0.476 (0.4367; 0.514)$\\
\hline
 $\text{HD}10700 $ & $-0.073 (-0.095; -0.0051)$ & $0.127 (0.105; 0.148)$ & $0.421 (0.403; 0.439)$ & $0.529 (0.513; 0.545)$ \\
\hline
 $\text{HD}215152 $& $-0.067 (-0.184; 0.052)$  & $0.269 (0.155; 0.376)$ & $0.210 (0.094; 0.321)$ & $-0.138 (-0.253; -0.020)$ \\
\hline
 $\text{Corot }7$ & $0.092 (-0.058; 0.238)$ & $-0.335 (-0.228; -0.082)$ & $-0.709 (0.626;0.776)$ & $0.595 (0.489; 0.683)$ \\
\hline
\rule{0pt}{2ex}    & & & &\\
\end{tabular}
\label{table:summaryStars}
\end{table*}
}

@@
